TGI-spinal-power

### 2022-06-24 analysis/tgispine_zoib_power-sim.Rmd
add burn to power calculation

## SIMULATIONS ##
# Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model
# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for both the cold and warm only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po_c <- data.frame()
po_w <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i)
    # simulating proportion of zero responses into the data using prop_zero (defined above)
    # this is a bit raw, but works!
    df_c <- prop_zero(df, 'cold')
    df_w <- prop_zero(df, 'warm')
    df_b <- prop_zero(df, 'burn')
    # bind all
    df_z <- rbind(df_c, df_w)
    df_z <- rbind(df_z, df_b)

@@

  # and the warm model based on simulated data
  m <- model(df_sim, 'warm')
  m2 <- summary(m)
  # extracting the p-value and effect size
  tmp1 <- c(m2$coefficients$cond[4,4], m2$coefficients$cond[4,1])
  po_w <- rbind(po_w,tmp1)
}

@@

write.csv(po_w, 'simulation_model_warm.csv', row.names = FALSE)
print(paste0('Warm power: ', round(power_w,2)))
```

>>>>

## SIMULATIONS ##
# Run through n = 1000 simulations of the pilot data, and extract p-value for the smallest effect (cold_location) of each model
# Extract the power from each model - first cold
```{r}
# the warm model has the smallest effect size, so should extract power calculation for both the cold and warm only
# do this for 40 participants, for 1000 simulations
nSims <- 1000
n <- 32 # number of participants to simulate
po_c <- data.frame()
po_w <- data.frame()
po_b <- data.frame()
for (i in 1:nSims){
  # creating individual data-frames from simulated data
  df_sim <- data.frame()
  for (i in 1:n) {
    df <- simulate_subj(i)
    # simulating proportion of zero responses into the data using prop_zero (defined above)
    # this is a bit raw, but works!
    df_c <- prop_zero(df, 'cold')
    df_w <- prop_zero(df, 'warm')
    df_b <- prop_zero(df, 'burn')
    # bind all
    df_z <- rbind(df_c, df_w)
    df_z <- rbind(df_z, df_b)

@@

  # and the warm model based on simulated data
  m <- model(df_sim, 'warm')
  m2 <- summary(m)
  # extracting the p-value and effect size
  tmp1 <- c(m2$coefficients$cond[4,4], m2$coefficients$cond[4,1])
  po_w <- rbind(po_w,tmp1)

  # then run the burn model based on simulated data
  m <- model(df_sim, 'burn')
  m1 <- summary(m)
  # extracting the p-value and effect size of cold location (our effect of interest)
  tmp <- c(m1$coefficients$cond[4,4], m1$coefficients$cond[4,1])
  po_b <- rbind(po_b,tmp)
}

@@

write.csv(po_w, 'simulation_model_warm.csv', row.names = FALSE)
print(paste0('Warm power: ', round(power_w,2)))

# then for burn
# some renaming
names(po_b)[1] <- 'pval'
names(po_b)[2] <- 'eff'
po_b$sig <- as.numeric(po_b$pval < .05) #is significant
po_b <- po_b[!is.na(po_b$sig) ,] #removing any NAs (models that did not converge) from the data frame

power_b <- sum(po_b$sig)/length(po_b$sig) # calculating power

write.csv(po_b, 'simulation_model_warm.csv', row.names = FALSE)
print(paste0('Burn power: ', round(power_b,2)))
```
